Title Goes Here

### 2020-04-17 analysis/paper/paper.Rmd
done with today

@@

making box plot by phase
```{r}
cv_plot <- cv_by_stage_df_unnest %>% 
  select(-data)

library(tidyr)
cv_plot %>% 
pivot_longer(cols = -SPstage.Stage, names_to = "group") %>% 
ggplot(aes(x = group, y = value, fill = as.factor(SPstage.Stage))) + 
geom_bar(stat="identity", position=position_dodge())

>>>>

Make a plot by site
```{r}
cv_plot_site <- cv_by_site_df_unnest %>% 
  select(-data)

library(tidyr)
cv_plot_site %>% 
pivot_longer(cols = -sitename, names_to = "group") %>% 
ggplot(aes(x = group, y = value, fill = as.factor(sitename))) + 
geom_bar(stat="identity", position=position_dodge())

@@

Make a plot by phase
```{r}
cv_plot_stage <- cv_by_stage_df_unnest %>% 
  select(-data)

library(tidyr)
cv_plot_stage %>% 
pivot_longer(cols = -SPstage.Stage, names_to = "group") %>% 
ggplot(aes(x = group, y = value, fill = as.factor(SPstage.Stage))) + 
geom_bar(stat="identity", position=position_dodge())
